Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-13 paper/ms.tex
starting to res-structure the final draft

\subsection{Additional  Constraints on the Occupation Fraction}

We impose an additional restriction using the observational results
by \cite{Hayes2010}. They constrained the value of $f_{\rm
  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the European Southern
Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
used in this \documentname the age of the universe between $z=3.1$ and
$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
conditions that determine the escape fraction $f_{\rm esc}$ and the
occupation fraction $f_{\rm  occ}$ remain similar over that time
scale.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
\end{center} 
\caption{Best models when both the constraints on the maximal number
  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
  0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
\end{figure*}

@@

@@

>>>>

@@

%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
%\hspace{5mm}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
%\end{center} 
%\caption{Best models when both the constraints on the maximal number
%  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
%  0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
%\end{figure*}

@@

In figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
for the {\tt match} method after applying the observational constraints 
in the occupation fraction and the ACF.

@@

\subsection{Observational estimates for the occupation fraction}

Observations by  \cite{Hayes2010} constrained the occupation fraction of $f_{\rm 
  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
European Southern 
Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
used in this \documentname the age of the universe between $z=3.1$ and
$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
conditions that determine the escape fraction $f_{\rm esc}$ and the
occupation fraction $f_{\rm  occ}$ remain similar over that time
scale.
